%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{hyperref}
\usepackage[left=0.65in,top=0.5in,right=0.65in,bottom=0.5in]{geometry} % Document margins

\name{Alex Sulsky} % Your name
\address{(917)~913~6586 \\ alex.sulsky@gmail.com} % Your phone number and email
\address{2727 Revere St, Houston, TX, 77098} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary address (optional)

\begin{document}

%----------------------------------------------------------------------------------------
%	BRIEF INTRO SECTION	
%----------------------------------------------------------------------------------------

\begin{rSection}{Brief}
Information security architect with experience building, protecting and automating resilient, distributed systems.
\end{rSection}
%------------------------------------------------

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION	
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Revel Sec}{October 2018 - Present}{Sr. Security Engineer}{Houston, TX}
  \begin{itemize}
  
     \item {Focus on enterprise security solutions using F5's Big-IP toolkit - LTM, GTM, APM and ASM.}
  
  \end{itemize}
\end{rSubsection}

\begin{rSubsection}{Independent Contractor}{June 2017 - October 2018 }{}{Houston, TX}
  \begin{itemize}
        \item F5 LTM, GTM, APM and ASM migration for a large healthcare provider in Texas.
        \item Firewall \& IPS log consolidation for SIEM consumption for a financial institution in Connecticut.
        \item IPS upgrade for a financial institution in Connecticut.
        \end{itemize}

\end{rSubsection}

\begin{rSubsection}{Macquarie Bank Ltd.}{May, 2015 - April, 2017}{Network Security Engineer - Contract}{Houston, TX}
  \begin{itemize}
        \item Built out and supported private and public cloud web-application and email delivery systems based on F5 LTM & GTM load balancing proxies.
        \item Final level of support for F5 load balancers and proxies as well as F5's APM network access control suite.
        \item Built out monitoring and reporting using Splunk and other off-the shelf systems, e.g. SiteScope.
        \item Built a web app to report on F5 LTM configuration and status using F5's iControl API.
        \item Worked with internal threat researchers to contain discovered exploits via custom rule-sets in McAfee Intrushield IPS.
  \end{itemize}

\end{rSubsection}

\begin{rSubsection}{Texas Children's Hospital}{October, 2011 - May, 2015}{Data Security Architect}{Houston, TX}
  \begin{itemize}
         \item Protected business-critical web applications with F5's Applications Security Manager. Set up ASM to detect and block OWASP's top 10 application layer attacks as well as, DOS, DDOS, bot-nets and brute forcing  attempts.
         
        \item Responsible for developing applications, systems \& network security solutions from concept to implementation.
        \item Served on the ``Architectural Review Committee'' to approve the design of proposed IT systems, create technical standards and advise policy.
        \item Built an application delivery system around F5's BIG-IP technologies using Global and Local Traffic Managers.
        \item Set up a centralized multi-factor authentication system for websites with a mix of F5's Access Policy Manager (APM) and RSA's Adaptive Authentication.
        \item Installed and configured F5's SAML-capable proxy to allow SSO with third-party applications.
        \item Built a DDOS mitigation scheme by peering with ISPs and incorporating Arbor's Pravail APS.
        \item Developed baseline security configurations for MS Windows 7, Linux \& AIX systems along with popular applications like MS Office, Internet Explorer \& Firefox applications on NIST and CIS Benchmarks.
        \item Set up Symantec's Control \& Compliance Suite to audit system compliance to configuration standards.
        \item Set up a meaningful risk assessment and reporting practice through the integration of Symantec's CCS with Symantec'۪s Data Leak Protection, Endpoint Protection, and Rapid 7'۪s Nexpose vulnerability scan results.
        \item Ran popular security tools including Checkpoint and Cisco firewalls, BlueCoat forward proxies, Rapid 7's and and RADIUS AAA servers.
        \item Set up phishing campaigns using Rapid 7's Metasploit.
  \end{itemize}
\end{rSubsection}

\begin{rSubsection}{Texas Children's Hospital}{May, 2011 - October, 2011}{Enterprise Systems Engineer - Contract}{Houston, TX}
  \begin{itemize}
        \item Worked on improving Microsoft Active Directory Services, PKI, and Microsoft Exchange systems.
        \item Integrated Wifi authentication with Active Directory through RADIUS \& 802.1x capable APs.
        \item Automated common administrative tasks through VBscript and PowerShell.
  \end{itemize}
\end{rSubsection}
%------------------------------------------------

\begin{rSubsection}{Alvarez \& Marsal}{February, 2007 - November, 2010}{Systems Engineer}{New York, NY}
%{At this global professional services firm, I was the lead for Microsoft Active Directory, Exchange, ISA and Windows Server platforms. I also:}
  \begin{itemize}
  	\item Lead for MS Active Directory and MS Exchange.
        \item Created detailed continuity and disaster recovery plans for messaging, DNS and web services.
        \item Managed encryption tools: PGP, Bitlocker, EFS, and SafEnd.
 %       \item Built data center storage systems for Exchange, VMWare, file share, and backup around EMC Clariion.
      %  \item Built branch office storage systems around FreeNAS, and HP StorageWorks.
  \end{itemize}
\end{rSubsection}
% \pagebreak
%------------------------------------------------
\begin{rSubsection}{Katzenbach Partners LLC }{December, 2002 - September, 2006}{Systems \& Networking Lead}{New York, NY}
%{As the technical lead at this management consulting firm, I deployed a majority of systems and networks.}
  \begin{itemize}
        \item Designed a highly available, multi-office WAN through dedicated inter-office frame relay links, backed by IPSec VPNs over the Internet.
        \item Designed on-premise datacenter, hosted infrastructure including data, management and storage networks.
        \item Led all Network, MS Active Directory \& MS Exchange-related work.
        \item Designed a multi-homed data center by way of BGP-peering with two ISPs.
        \item Built a multi-site WLAN around Cisco APs and Active Directory-based authentication.
        \item Automated desktop deployment using Microsoft's Remote Installation Server and distributed filesystem storage.
        \item Secured systems, firewalls, and networking equipment using NSA, NIST, and vendor guidelines.
        \item Managed SonicWall/NetStructure, and Cisco firewalls.
	\item Migrated from 3M /Motorola/Intel network to Cisco switches and routers.
        \item Set up detailed network monitoring.
  \end{itemize}
\end{rSubsection}
%----------------------------------------------------------------------------------------
\begin{rSubsection}{Comtex}{1997 - 2001}{Desktop, Server Support}{New York, NY}
% \item Maintained WindowsNT servers
% \item Wrote user logon and usage reporting shell scripts
\end{rSubsection}
\end{rSection}
\pagebreak

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS SECTION
%----------------------------------------------------------------------------------------
 \begin{rSection}{Certifications}{}
     \item CISSP \#394506
     \item Microsoft Certified Professional \#6310169
     \item Palo Alto Accredited Configuration Engineer
 \end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
 \begin{rSection}{Education}
 \begin{rSubsection}{Digital Crafts}{September, 2017 - January, 2018}{Student}{Houston, TX} 
 	Accelerated School for Software Engineering - Full Stack Immersive Program
  	\begin{itemize}
	\item {Introduced to application development using popular JavaScript and Python frameworks such as NodeJS, jQuery, 	React, Express, Flask, Tornado.}
	\item {Worked with Postgresql and Firebase databases.}
	\item {DevOps with AWS, Heroku, Dokku and Git.}
	\item Built and deployed web applications using the above tools.
	\item GitHub: {https://github.com/xanlex/}

 \end{itemize}
\end{rSubsection}


 {\bf Brooklyn College, CUNY} \hfill {\em June 2001} \\ 
 	B.S. in Computer Science (Incomplete)

 \end{rSection}
% ----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------
% \begin{rSection}{Technical Strengths}
% \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }

% Protocols \& Standards & AAA; RADIUS; LDAP; ADSI; IPSec; PKI; SSL/TLS \\
% & SSL VPN; DHCP; DNS; PGP; SAML;  SNMP; sFlow; \\ 
% Systems \& Tools & Load Balancers and Proxies; RSA's Adaptive Authentication\\
% & Nexpose; Firewalls; Nmap; Wireshark; Windows \& Linux\\
% Scripting \& API's & PowerShell; Bash\\
% GRC & ITIL; PCI; HIPAA; NIST; Risk Assessment; Vulnerability Assessment\\
% & Policy Development; Compliance Assessment; System Baseline standards\\
% \end{tabular}

% \end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Technical Strengths}

%System, Web, and Network Security; High Availability Infrastructure; Application Delivery Infrastructure.


%\end{rSection}

%----------------------------------------------------------------------------------------


\end{document}